The paper on \Large \bf Blockchain Frontrunning

### 2018-08-27 frontrunning/Latex/sections/paper.tex
[frontrunning]double spend

\subsection{Recent Literature on Blockchain front-running}

A few researchers discussed front-running in the context of blockchain and decentral ledgers.

Aune~\etal\cite{aune2017footprints} discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage. As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach to prevent any decentralized system from front-running. In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.

@@

>>>>

\subsection{Recent Literature on Blockchain front-running}
%NOTE (ASK JEREMY): decentral or decentralized?
There are only a few research carried out on the front-running subject in the context of blockchain and decentral ledgers. 
Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach to prevent any decentralized system from front-running. In this approach, which is similar to commit and reveal, a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.

@@

Some researchers have discussed the double spending attack on the Bitcoin blockchain. In this attack, as the name implies, the adversary spends a coin more than one time. To do so, he would use the coin as an input of a transaction and broadcast it to the network, before the transaction gets validated and executed, he broadcasts another transaction associated with a higher transaction fee which spends the same input ~\cite{bamert2013have, karame2012double}. This adversarial behaviour is similar to the front-running attack where the attacker would front-run other users by paying a higher gas price when broadcasting his transactions to the network.  As mentioned above, this leads to the faster execution of the transaction on the Ethereum blcokchain.
